\documentclass[12pt]{article}
\usepackage[dvips]{graphicx}
\usepackage{setspace,palatino,multirow}
\usepackage{amsmath,amssymb}
\usepackage{amsthm}
\usepackage{subfig,comment}
\usepackage{pdflscape}
\usepackage[dvipsnames]{xcolor}
\usepackage{hyperref}
\usepackage[longnamesfirst]{natbib}
\bibliographystyle{chicago}

\special{papersize=8.5in,11in}

\definecolor{darkred}{rgb}{0.66,0,0}
\definecolor{darkblue}{rgb}{0,0,0.25}

\hypersetup{
  colorlinks=true,
  citecolor=darkblue,
  linkcolor=darkblue,
  pdfpagemode=none,
  pdfstartview={FitH},
  pdftitle={},
  pdfauthor={},
  pdfkeywords={}
}

\setlength{\parindent}{0.25in}
\setlength{\parskip}{1.5ex plus0.5ex minus0.5ex}
\textwidth15.75cm
\evensidemargin5mm
\oddsidemargin5mm
\topmargin-15mm
\textheight 22.7cm
\hyphenation{over-lapping}

\renewcommand{\arraystretch}{1.1}
\usepackage[margin=2cm]{geometry}

\newcounter{saveeqni}%
\newcounter{saveeqn01i}%
\newcommand{\alpheqni}{\setcounter{saveeqni}{\value{section}}%
\renewcommand{\theequation}
    {\alph{saveeqni}\mbox{.\arabic{equation}}}}%
\newcommand{\reseteqni}{\setcounter{equation}{\value{saveeqni}}%
\renewcommand{\theequation}{\arabic{equation}}}%

\begin{document}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\theoremstyle{definition}
\newtheorem{result}{Result}
\theoremstyle{plain}
\newtheorem{lemma}{Lemma}
\theoremstyle{plain}
\newtheorem{proposition}{Proposition}
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\theoremstyle{plain}
\newtheorem{corollary}{Corollary}

\begin{onehalfspacing}

\vspace{1.0cm}

\noindent \textbf{Reply to Referee 1 of the manuscript ``Resolving Coordination Frictions in Green Labor Transitions: Minimizing Unemployment, Costs, and Welfare Distortions.''}

\bigskip

Dear Referee,

\medskip

Thank you very much for your careful reading and highly constructive report. We are grateful for both your two essential comments and your detailed smaller suggestions. We revised the manuscript to address all points in a systematic way.

In what follows, we reproduce each comment in bold and provide our response directly below it.

Before turning to the comment-by-comment responses, we summarize the main revisions:

\textbf{First}, we strengthened the transition section by clarifying what is and is not claimed under the sequence-of-steady-states approach, and by adding quantitative diagnostics to evaluate transition speed after policy shocks.

\textbf{Second}, we expanded the calibration/identification discussion with a clearer parameter-to-moment mapping and additional intuition for why key moments are most informative for specific parameters.

\textbf{Third}, we implemented all editorial and presentation changes requested (terminology, figure presentation, framing, and section-level clarity), and clarified several ambiguous statements in the calibration and policy discussion.

We now move to the specific comments.

\bigskip
\bigskip

\textbf{Comment 1 (Essential): Transition dynamics. I am satisfied with the way the paper models the green transition as a sequence of steady states. That said, this will seem more plausible if the paper can show that the economy transitions quickly to a new steady state after unexpected policy shifts (e.g., MIT shocks).}

\medskip

Thank you for this important suggestion. We agree this is central for interpretation. We now add a quantitative transition-speed exercise after unanticipated policy changes and report convergence metrics (including [INSERT METRICS]). These results support the practical use of a sequence-of-steady-states approximation in our setting.

\bigskip
\bigskip

\textbf{Comment 2 (Essential): Identification. The paper maps parameters to targeted moments, but needs a clear and intuitive explanation of this mapping. It would help to show how key moments vary when key parameters change.}

\medskip

Thank you for this valuable point. We expanded the identification discussion and now provide an intuitive mapping from parameters to moments, including why some moments are more sensitive to specific parameters. We also add sensitivity evidence (tables/figures) showing how key targeted moments move with parameter variation.

\bigskip
\bigskip

\textbf{Comment 3 (Smaller): Clarify that a hiring likelihood ratio of 1.29 means ``29\% higher than for other workers.''}

\medskip

Implemented. We now state this explicitly in the calibration paragraph and align wording with the value in the table.

\bigskip
\bigskip

\textbf{Comment 4 (Smaller): The statements ``using 2022 generation is conservative given the near-term pipeline'' and ``the higher benchmark provides a fiscal stress test'' are unclear.}

\medskip

Thank you. We rewrote this passage to define both phrases precisely and to explain the logic in transparent, quantitative terms.

\bigskip
\bigskip

\textbf{Comment 5 (Smaller): Why does calibration use a 2023 unemployment rate of 3.5\% while claiming calibration to the 2022 labor market?}

\medskip

Thank you for catching this inconsistency. We corrected and clarified the date convention in the calibration section and ensured internal consistency across text, targets, and tables.

\bigskip
\bigskip

\textbf{Comment 6 (Smaller): Under Table 3, ``three policy paths'' should be ``three policy mixes'' (or equivalent), since these are not paths yet.}

\medskip

Implemented. We replaced this language and now consistently refer to these as policy mixes/configurations at a fixed target.

\bigskip
\bigskip

\textbf{Comment 7 (Smaller): In Figure 7, why are bars not the same width?}

\medskip

Thank you. We revised the figure rendering to ensure consistent bar widths and improved visual readability.

\bigskip
\bigskip

\textbf{Comment 8 (Smaller): The key takeaway from Figure 7 appears to be the strong rotation in policy mix versus relatively stable total intervention size; hump-shape seems second-order.}

\medskip

We agree and revised the text accordingly. The discussion now emphasizes composition rotation as the primary mechanism/result, with the hump profile presented as a secondary quantitative feature.

\bigskip
\bigskip

\textbf{Comment 9 (Smaller): Writing in Section 4.3.1 is somewhat convoluted.}

\medskip

Thank you. We rewrote this subsection for clarity, shortening dense passages and improving signposting of the economic mechanism.

\bigskip
\bigskip

\textbf{Comment 10 (Smaller): Policy intervention sizes are likely an upper bound because technical change may raise green productivity/wages and younger cohorts may face lower entry costs over time.}

\medskip

We agree and now add explicit upper-bound framing and interpretation in the discussion/conclusion, including why this does not overturn the core instrument-design ranking.

\bigskip
\bigskip

\textbf{Comment 11 (Smaller): Figure D.8 in the appendix is very illustrative and may deserve to be in the main text.}

\medskip

Thank you for this suggestion. We moved [INSERT FIGURE ID] to the main text (or cross-referenced it more prominently, depending on space constraints) and updated the surrounding discussion.

\bigskip

We again thank you for the insightful and constructive feedback. It substantially improved both the clarity and the policy relevance of the revised manuscript.

\end{onehalfspacing}
\end{document}
